---
title: "Software to manage Camera Trapping Images"
subtitle: "Survey Results"
output: github_document

---

```{r,warning=FALSE,message=FALSE, echo = FALSE}
library(tidyverse)
library(googledrive)
knitr::opts_chunk$set(echo = FALSE)

theme_set(theme_light())
```

```{r, message = FALSE}

googledrive::drive_download(as_id("https://docs.google.com/spreadsheets/d/1DTioHEcN88Iy7H4mKSnW81VfcwlKZBDZXQGSnJkWgKk/edit?usp=sharing"),type = "csv",path = "responses", overwrite = T)

responses <- read_csv("responses.csv") %>%
  mutate(Timestamp = parse_datetime(Timestamp,format = "%d/%m/%Y %H:%M:%S"))

responses_tidy <- responses %>%
  gather(question,answer,-1) %>%
  mutate(
    question = str_replace(question,"sofware","software"),
    answer = str_remove(answer," / no dedicated software")
    ) %>%
  mutate(
    question_cat = case_when(
      grepl("other software",question)~"Software text",
      grepl("different environment",question)~"Environment text",
      grepl("What environment",question)~"Environment factor",
      grepl("What software",question)~"Software factor"
    )
  ) %>%
  separate(question_cat,c("category","type")," ")

```


Here are the Results from [the survey](https://forms.gle/uafXkWzh8FinCsv86) *Software to manage Camera Trapping Images* posted on [wildlabs.net](https://www.wildlabs.net/community/thread/688) on 21.03.2019 and shared via [Twitter](https://twitter.com/WILDLABSNET/status/1108676937868812288?s=20) subsequently. We received `r nrow(responses)` to date (`r Sys.Date()`). The survey consisted of four questions:

1. What software do you use to mange your camera trapping images?
1. If you use other software, please comment
1. What environment do you work in?
1. If you work in a different environment, please specify




```{r, fig.cap="Number of responses per day"}
responses %>%
  ggplot(aes(Timestamp)) + 
  geom_histogram(binwidth = 3600*24, fill = "grey",colour = "black") +
  labs(y = "Number of responses",x = "Date")


```



## Question No 1

> What software do you use to mange your camera trapping images?

(multiple answers possible)

```{r}
responses_tidy %>%
  filter(type == "factor") %>%
  filter(category == "Software") %>%
  separate_rows(answer, sep = ", ") %>% 
  group_by(question,answer) %>%
  count() %>%
  ungroup() %>%
  mutate(
    answer = fct_reorder(answer,n),
    answer = fct_relevel(answer,"other",after = 0L)
  ) %>%
  ggplot(aes(answer,n)) + 
  geom_col() +
  scale_y_continuous(breaks = 0:15) +
  labs(y = "Number of responses") +
  theme(axis.title.y = element_blank()) + 
  coord_flip() 


```

## Question No 2

> If you use other software, please comment:

```{r,results='asis'}
responses_tidy %>%
  filter(!is.na(answer)) %>%
  filter(type == "text") %>%
  filter(category == "Software") %>%
  pull(answer) %>%
  pander::pandoc.list()

```

(the above is a list of all non-empty responses)

## Question No 3


> What environment do you work in?

```{r}
responses_tidy %>%
  filter(type == "factor") %>%
  filter(category == "Environment") %>%
  separate_rows(answer, sep = ", ") %>% 
  group_by(question,answer) %>%
  count() %>%
  ungroup() %>%
  mutate(
    answer = fct_reorder(answer,n)
  ) %>%
  ggplot(aes(answer,n)) + 
  geom_col() +
  scale_y_continuous(breaks = 0:15) +
  labs(y = "Number of responses") +
  theme(axis.title.y = element_blank()) +
  coord_flip()

```


## Question No 4

> If you work in a different environment, please specify:


```{r}
all_na <- responses_tidy %>%
  filter(type == "text") %>%
  filter(category == "Environment") %>%
  pull(answer) %>%
  is.na() %>%
  `!` %>%
  any()


```

`r ifelse(!all_na,"(No responses)","Some responses, redo analysis")`

